\begin{command}[@FWR/MsensHcl]{MsensH\_cl}	\desc{Purpose}Compute the closed-loop transfer function sensitivity measure (and thesensitivity matrix)	\desc{Syntax}\matlab{[M MZ]  = MsensH\_cl( R, Sysp)}	\desc{Parameters}		\begin{tabular}{l@{\ :\ }p{9cm}}\matlab{M} &  sensitivity measure        \\\matlab{MZ} &  sensitivity matrix        \\\matlab{R} &  FWR object                 \\\matlab{Sysp} &  plant system (ss object)\\		\end{tabular}	\desc{Description}The closed-loop transfer function sensitivity measure is very similar to the open-loop transfer function sensitivity. It is defined by\begin{equation}\bar{M}_{L_{2}}^W = \norm{\dede{\bar{H}}{Z} \times r_{Z}}_{F}^2.\end{equation}where $\dede{\bar{H}}{Z}\in\Rbb{l+n+p}{l+n+q}$ is the \I{transfer function sensitivity matrix}.It is the matrix of the $L_{2}$-norm of the sensitivity of the transfer function $\bar{H}$ withrespect to each coefficient  $Z_{i,j}$. It is defined by\begin{equation}\pa{\dede{\bar{H}}{Z}}_{i,j} \triangleq \norm{\dd{\bar{H}}{Z_{i,j}}}_{2},\end{equation}In SISO case, the $\bar{M}_{L_{2}}^W$ measure is equal to\begin{equation}\bar{M}_{L_{2}}^W = \norm{\dd{\bar{H}}{Z} \times r_{Z}}_2^2.\end{equation}The $M_{L_2}^W$ measure can be evaluated by the followingpropositions\cite{Hila07d}\begin{proposition}\begin{equation}\dd{\bar{H}}{Z} =  \bar{H}_1 \cd \bar{H}_2\end{equation}where $H_1$ and $H_2$ are defined by\begin{eqnarray}\bar{H}_1 : z &\mapsto& \bar{C}\pa{ zI-\bar{A} }^{-1} \bar{M}_1 + \bar{M}_2 \\\bar{H}_2 : z &\mapsto& \bar{N}_1 \pa{ zI-\bar{A} }^{-1}\bar{B} + \bar{N}_2\end{eqnarray}with\begin{eqnarray}\bar{M}_1 = \begin{pmatrix}B_2LJ^{-1} & 0 & B_2 \\KJ^{-1} & I_n & 0\end{pmatrix} &&\bar{N}_1 =\begin{pmatrix}J^{-1}NC_2 & J^{-1}M \\0 & I_{n} \\C_2 & 0\end{pmatrix}\\\bar{M}_2 = \begin{pmatrix} D_{12}LJ^{-1} & 0 & D_{12} \end{pmatrix} &&\bar{N}_2 = \begin{pmatrix} J^{-1}ND_{21} \\ 0 \\ D_{21} \end{pmatrix}\end{eqnarray}\end{proposition}\desc{See also}\funcName[@FWR/MsensH]{MsensH}, \funcName[@FWR/wprodnorm]{w\_prod\_norm}	\desc{References}\cite{Hila07d}	T. Hilaire and P. Chevrel. On the compactformulation of the derivation of a transfer matrix with respect toanother matrix. Technical Report RR-6760, INRIA, 2008.\\\cite{Hila07e}	T. Hilaire, P. Chevrel, and J. Whidborne. Lowparametric closed-loop sensitivity realizations using fixed-pointand floating-point arithmetic. In Proc. European Control Conference (ECC'07), July 2007.\\\cite{Hila08b}	T. Hilaire, P. Chevrel, and J. Whidborne. Finitewordlength controller realizations using the specialized implicitform. Technical Report RR-6759, INRIA, 2008.\\\end{command}