\begin{command}[@FWR/relaxedl2scaling]{relaxedl2scaling}	\desc{Purpose}Perform a relaxed-$L_2$-scaling on the FWR.The wordlength are deduced from the FPIS if it is defined.	\desc{Syntax}\matlab{R = lrelaxedl2scaling(R,Umax,delta)     }\\\matlab{[U,Y,W] = relaxedl2scaling(R,Umax,delta)}	\desc{Parameters}		\begin{tabular}{l@{\ :\ }p{9cm}}\matlab{R} &  FWR object                                               \\\matlab{U,Y,W} &  transformation matrices applied on R                 \\\matlab{Umax} &  input maximum magnitude (default: Umax = a power of 2)\\\matlab{delta} &  security parameter (default: delta=1)                \\		\end{tabular}	\desc{Description}Perform a relaxed-$L_2$-scaling.\\The scaling forces the transfer functions from the inputs to the states and the intermediates variables to have a $L_2$-norm between 1 and 4. Theses norms are given by the diagonal terms of $W_c$ and $J^{-1}\pa{NN^\top+MW_cM^\top}J^{-\top}$.\\Denote $W_{cX}$ the controllability gramian of the realization ($W_c$) and $W_{cT}$ the controllability gramian related to the intermediate variables. It is given by\begin{equation}W_{cX} = \sqrt{\pa{J^{-1}\pa{NN^\top+M W_{cX} M^\top}J^{-\top}}}\end{equation}The relaxed-$L_2$-scaling is a transformation that make the realization satisfy the constraints ($\forall 1 \leq i \leq n$)\begin{eqnarray}\frac{2^{2{\alpha_X}_i}}{\delta^2} \leq &\pa{W_{cX}}_{i,i}& < 4 \frac{2^{2{\alpha_X}_i}}{\delta^2} \\\frac{2^{2{\alpha_T}_i}}{\delta^2} \leq &\pa{W_{cT}}_{i,i}& < 4 \frac{2^{2{\alpha_T}_i}}{\delta^2}\end{eqnarray}where\begin{eqnarray}{\alpha_X}_i &\triangleq& \beta_{X_i}-\beta_U-\mathscr{F}_2\pa{\overset{\max}{U}} \\{\alpha_T}_i &\triangleq& \beta_{T_i}-\beta_U-\mathscr{F}_2\pa{\overset{\max}{U}}\end{eqnarray}and $\mathscr{F}_2(x)$ is defined as the fractional value of $\log_2(x)$:\begin{equation}\mathscr{F}_2(x)\triangleq \log_2(x) - \left\lfloor \log_2(x) \right\rfloor\end{equation}If the wordlength $\beta_X$ and $\beta_T$ are not defined by the FPIS, they are also supposed to be equal. Moreover, if $\delta=1$ (default case) and $\overset{\max}{U}$ isa power of $2$, then the realization satisfies the following constraints\begin{equation}1 \leq (W_{cX})_{ii} < 4, \hspace{1cm} 1 \leq (W_{cT})_{ii} < 4, \hspace{1cm} \forall 1\leq i \leq n\end{equation}The $L_2$-scaling is achieved by a $\mt{U}\mt{Y}\mt{W}$-transformation where $\mt{U}$ and $\mt{W}$ are diagonal with:\begin{eqnarray}\pa{\mt{U}}_{ii} &=& \delta \sqrt{\pa{W_{cX}}_{i,i}} 2^{-\mathscr{F}_2(\delta\sqrt{\pa{W_{cX}}_{i,i}})-{\alpha_X}_i} \\\pa{\mt{W}}_{ii} &=& \delta \sqrt{\pa{W_{cT}}_{i,i}} 2^{-\mathscr{F}_2(\delta\sqrt{\pa{W_{cT}}_{i,i}})-{\alpha_T}_i}\end{eqnarray}\desc{See also}\funcName[@FWR/l2scaling]{l2scaling}	\desc{References}\cite{Feng09a} Y. Feng, P. Chevrel, and T. Hilaire. A practical strategy of an efficient and sparse fwl implementation of lti filters. In submitted to ECC?09, 2009.\\\cite{Hila09a}	T. Hilaire. Low parametric sensitivity realizations with relaxed l2-dynamic-range-scaling constraints. submitted to IEEE Trans. on Circuits \& Systems II, 2009.\end{command}