\begin{command}[@FWS/MsensPole]{MsensPole}	\desc{Purpose}Compute the open-loop pole sensitivity measure for a FWS object.The computation is based on the UYW-transform	\desc{Syntax}\matlab{M = MsensPole( S, U,Y,W, moduli)}	\desc{Parameters}		\begin{tabular}{l@{\ :\ }p{9cm}}\matlab{M} &  pole sensitivity measure                                                                                    \\\matlab{S} &  FWS object                                                                                                  \\\matlab{U,Y,W } &  transformation matrices                                                                                \\\matlab{moduli } &  1 (default value) : compute $\dd{\abs{\lambda}}{Z}$ (the sensitivity of the moduli of the eigenvalues)\\\matlab{} &  0 : compute $\dd{\lambda}{Z}$ (without the moduli)                                                           \\		\end{tabular}	\desc{Description}This function computes the open-loop pole sensitivity measure for a FWS object. It is based on the $\mt{UYW}$-transform.If we consider $\mt{T}_1$ and $\mt{T}_2$ such that\begin{equation}Z_1 = \mt{T}_1	Z_0 \mt{T}_2\end{equation}\begin{equation}\mt{T}_1 = \begin{pmatrix}\mt{Y}\\&\mt{U}^{-1}\\&&I_{p}\end{pmatrix}, \hspace{5mm}\mt{T}_2 = \begin{pmatrix}\mt{W}\\&\mt{U}\\&&I_{m}\end{pmatrix}\end{equation}then the sensitivity measure for $Z_1$ can be computed from the sensitivity for $Z_0$ with\begin{equation}\en{ \dd{\abs{\lambda_k}}{Z} }_{Z_1} =  \mt{T}_1^{-\top} \en{ \dd{\abs{\lambda_k}}{Z} }_{Z_0} \mt{T}_2^{-\top}\end{equation}These matrix $\en{ \dd{\abs{\lambda_k}}{Z} }_{Z_0}$ are stored in the \matlab{dataMeasure} field.\desc{See also}\funcName[@FWS/MsensPolecl]{MsensPole\_cl}, \funcName[@FWR/MsensPole]{MsensPole}	\desc{References}\cite{Hila06b}	T. Hilaire, P. Chevrel, and J.-P. Clauzel. Polesensitivity stability related measure of FWL realization with theimplicit state-space formalism. In 5th IFAC Symposium on Robust Control Design (ROCOND'06), July 2006.\\\cite{Hila07b}	T. Hilaire, P. Chevrel, and J. Whidborne. A unifying framework for finite wordlength realizations. IEEE Trans. on Circuits and Systems, 8(54), August 2007.\end{command}